Peridynamic Beams: \\ A Non-ordinary, State Based Model

### 2014-02-05 BeamPaper.tex
clarified eringen equivalence and changed more y displacements to v

Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material.
\begin{equation}
\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}')\notag
\end{equation}
In the local limit these relationships take the form of higher-order gradients.
Using a modified bessel function (second kind) nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
\begin{align}
\left(1-\tau^2l^2\nabla^2\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
\end{align}
in which \(\tau^2l^2\) is a scale-based material parameter.
For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\tau^2l^2\) we can see that this relationship could be reformulated as
\begin{equation}
\mathbf{t}=\left(1+\tau^2l^2\nabla^2\right)\boldsymbol{\sigma}.\notag
\end{equation}

>>>>

Eringen's model for nonlocal elasticity in \cite{eringen1983differential} begins with a nonlocal modulus (denoted here as \(K(|\mathbf{x}'-\mathbf{x}|,\tau)\)) that relates the nonlocal stress \(\mathbf{t}\) at a point to the classical (local) stress \(\boldsymbol{\sigma}\) in the nearby material through the integral
\begin{equation}
\mathbf{t} = \int_\mathbf{V} K(|\mathbf{x}'-\mathbf{x}|,\tau)\sigma(\mathbf{x}')dv(\mathbf{x}').\notag
\end{equation}
In the local limit these relationships take the form of higher-order gradients.
Using a decaying exponential nonlocal modulus results in a relationship between \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) 
\begin{align}
\left(1-\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\mathbf{t}&=\boldsymbol{\sigma},\notag
\end{align}
in which \(\tau^2l^2\) is a scale-based material parameter.
For well-behaved \(\mathbf{t}\) and \(\boldsymbol{\sigma}\) and small values of \(\sigma''''\) and \(\tau^2l^2\), we can see that this relationship could be reformulated as
\begin{equation}
\mathbf{t}=\left(1+\tau^2l^2\frac{\partial^2}{\partial x^2}\right)\boldsymbol{\sigma}.\notag
\end{equation}
